Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-05-26 src/tex/ms.tex
Moved two_moons to a two column figure.
Updated two_moons example plot.
Wrote caption for the two moons figure.

\note{Two moons example figure. Need to convert this to a uniform distribution.}
\begin{figure}[ht!]
    \script{two_moons_example.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/twomoons_example.pdf}
        \caption{
            Need to write!
        }
        \label{fig:two-moons}
    \end{centering}
\end{figure}

@@

If we further assume that is invertible, we can sample from the data distribution by appling $f^{-1}$ to samples from the latent distribution:
\begin{align}
    x = f^{-1} \quad \text{where} \quad u \sim \pu.
\end{align}

@@

The following sections discuss how to build a normalizing flow to model data with various features.
Section \ref{sec:bijections} discusses the bijection $f$ and introduces the building blocks from which our bijections will be built;
Section \ref{sec:latent} discusses how to choose an appropriate latent distribution for your data;
Section \ref{sec:conditional} describe how to condition a normalizing flow on some conditional variables;
Section \ref{sec:periodic} explains how to model data with periodic topology;
finally Section \ref{sed:discrete} explains how to model data with discrete variables.

@@

\subsubsection{Rational-Quadratic Rolling Spline Couplings (RQ-RSCs)}
\label{sec:rq-rsc}

>>>>

\begin{figure*}[t!]
    \script{plot_two_moons.py}
    \begin{centering}
        \includegraphics{figures/twomoons_example.pdf}
        \caption{
            A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn}.
            The two moons data on the left is mapped onto a two dimensional uniform distribution by the bijection $f$.
            The data are colored by quadrant to visualize their image in the latent space.
            You can sample the data distribution by sampling from the uniform distribution, and using $f^{-1}$ to map the back to the data space.
        }
        \label{fig:two-moons}
    \end{centering}
\end{figure*}

@@

If we further assume that is invertible, we can sample from the data distribution by appling $f^{-1}$ to samples from the latent distribution:
\begin{align}
    x = f^{-1}(u) \quad \text{where} \quad u \sim \pu.
\end{align}

@@

The following sections discuss how to build a normalizing flow to model data with various features.
Section \ref{sec:bijections} discusses the bijection $f$ and introduces the building blocks from which our bijections will be built;
Section \ref{sec:latent} discusses how to choose an appropriate latent distribution for your data;
Section \ref{sec:conditional} describe how to condition a normalizing flow on some conditional variables;
Section \ref{sec:periodic} explains how to model data with periodic topology;
finally Section \ref{sec:discrete} explains how to model data with discrete variables.

@@

\subsubsection{Rational-Quadratic Rolling Spline Couplings}
\label{sec:rq-rsc}
